The importance of alternatives in scalar implicature

### 2016-01-23 Paper/Paper.Rmd
relative plots

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

@@

```{r helpers}
path <- "~/Desktop/Projects/scalar_implicature/models/"
normedVec <- function(vec) vec / sum(vec)
```

```{r, data}
# All scales studied
# ------------------
scales <- c("good_excellent",
            "liked_loved",
            "palatable_delicious",
            "memorable_unforgettable",
            "some_all")
# Experiment E9: Alternatives
# ---------------------------
alternativesData <- read.csv(paste(path, "model_data/e9_alternativeCounts.csv", sep = ""),
                             stringsAsFactors = FALSE)
allModelRunData <- read.csv(paste(path, "model_data/allModelRuns.csv", sep = ""),
                     stringsAsFactors = FALSE)

# Experiments E8, E10, E12: Literal listener
# ------------------------------------------
speakerE12 <- read.csv(paste(path, "model_data/L0_e12.csv", sep  = ""), stringsAsFactors = FALSE)
speakerE10 <- read.csv(paste(path, "model_data/L0_e10.csv", sep = ""), stringsAsFactors = FALSE)
speakerE8 <- read.csv(paste(path, "model_data/L0_e8.csv", sep = ""), stringsAsFactors = FALSE)
# Experiments E6, E11: Pragmatic listener
# ---------------------------------------
listenerE6 <- read.csv(paste(path, "model_data/L1_e6.csv", sep = ""), stringsAsFactors = FALSE)
listenerE11 <- read.csv(paste(path, "model_data/L1_e11.csv", sep = ""), stringsAsFactors = FALSE)
```

@@

# Screen shots of literal listener and pragmatic listener conditions
grid::grid.raster(png::readPNG("~/Desktop/Projects/scalar_implicature/Paper/figs/exp1_stimuli.png"))
```

@@

# Scale stimuli
grid::grid.raster(png::readPNG("~/Desktop/Projects/scalar_implicature/Paper/figs/alternativeSets.png"))
```

>>>>

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=TRUE, message=F, sanitize = T)
```

@@

```{r helpers}
normedVec <- function(vec) vec / sum(vec)
```

```{r, data}
# All scales studied
# ------------------
scales <- c("good_excellent",
            "liked_loved",
            "palatable_delicious",
            "memorable_unforgettable",
            "some_all")
# Experiment E9: Alternatives
# ---------------------------
alternativesData <- read.csv("../models/model_data/e9_alternativeCounts.csv",
                             stringsAsFactors = FALSE)
allModelRunData <- read.csv("../models/model_data/allModelRuns.csv",
                     stringsAsFactors = FALSE)

# Experiments E8, E10, E12: Literal listener
# ------------------------------------------
speakerE12 <- read.csv("../models/model_data/L0_e12.csv", stringsAsFactors = FALSE)
speakerE10 <- read.csv("../models/model_data/L0_e10.csv", stringsAsFactors = FALSE)
speakerE8 <- read.csv("../models/model_data/L0_e8.csv", stringsAsFactors = FALSE)
# Experiments E6, E11: Pragmatic listener
# ---------------------------------------
listenerE6 <- read.csv("../models/model_data/L1_e6.csv", stringsAsFactors = FALSE)
listenerE11 <- read.csv("../models/model_data/L1_e11.csv", stringsAsFactors = FALSE)
```

@@

# Screen shots of literal listener and pragmatic listener conditions
grid::grid.raster(png::readPNG("figs/exp1_stimuli.png"))
```

@@

# Scale stimuli
grid::grid.raster(png::readPNG("figs/alternativeSets.png"))
```
